Preserving Reciprocal Consistency in \\ Distributed Graph Databases

### 2020-04-20 slides/figures/hc-edge.tex
corrections

\begin{tikzpicture}[node distance=2.2cm]
  \node (rect)  [draw,rounded corners,minimum width=3.5cm,minimum height=4cm,label=above:{$S_i$}] {};
  \node (rect)  [draw,rounded corners,minimum width=3.5cm,minimum height=4cm,label=above:{$S_j$},xshift=6cm] {};
  \node (v1) [big_vertex,xshift=0cm,yshift=0cm] {\small{\texttt{a:\textcolor{green}{Person}}}};
  \node (v2) [big_vertex,xshift=6cm,yshift=0cm] {\small{\texttt{b:\textcolor{green}{Book}}}};
  \node [below of=v1,yshift=1cm] {\small{\texttt{\textcolor{red}{name}:Tolkien}}};
  \node [below of=v2,yshift=1cm] {\small{\texttt{\textcolor{red}{title}:The Hobbit}}};
  \draw [thick,dashed,->,>=stealth] (0.9,0)  -- node [midway,above] {:\textcolor{green}{\small{\texttt{WROTE}}}} (5.1,0);
\end{tikzpicture}

>>>>

\begin{tikzpicture}[node distance=2.2cm]
    \node (rect)  [draw,rounded corners,minimum width=3.5cm,minimum height=4cm,label=above:{$S_i$}] {};
  \node (rect)  [draw,rounded corners,minimum width=3.5cm,minimum height=4cm,label=above:{$S_j$},xshift=5.6cm] {};
  \node (v1) [big_vertex,xshift=0cm,yshift=0cm] {\small{\texttt{a:\textcolor{green}{Person}}}};

  \node (v2) [big_vertex,xshift=5.6cm,yshift=0cm] {\small{\texttt{b:\textcolor{green}{Book}}}};

  \node [below of=v1,yshift=1cm] {\small{\texttt{\textcolor{red}{name}:Tolkien}}};
  \node [below of=v2,yshift=1cm] {\small{\texttt{\textcolor{red}{title}:The Hobbit}}};

  \draw [thick,dashed,->,>=stealth] (0.9,0)  -- node [midway,above] {:\textcolor{green}{\small{\texttt{WROTE}}}} node [midway,below,xshift=0.1cm] {\small{\texttt{\textcolor{red}{year}:1937}}} (2.7,0);
\end{tikzpicture}

### 2020-04-20 slides/figures/hc-storage.tex
corrections

  \node (v1) [draw,black,minimum height=0.9cm,minimum width=1cm,text width=0.4\linewidth,xshift=-4.3cm,align=center,yshift=0cm] {\small{\texttt{vertex id}}};

@@

      \node (1i1)  [draw,black,minimum height=0.6cm,minimum width=2cm,xshift=-0.5cm,text width=0.6\linewidth,yshift=0cm,align=center] {\small{\texttt{edge}}};

      \node (1i2)  [draw,black,minimum height=0.6cm,minimum width=2cm,xshift=1.9cm,yshift=0cm,right of = 1i1,text width=0.6\linewidth,align=center] {\small{\texttt{edge}}};

  % 2
  \node (v) [draw,black,minimum height=0.9cm,minimum width=1cm,text width=0.4\linewidth,xshift=-4.3cm,align=center,yshift=-1.2cm] {\small{\texttt{b:Book}}};

@@

  \node (2i1)  [draw,black,minimum height=0.6cm,minimum width=2cm,xshift=-0.5cm,text width=0.6\linewidth,yshift=-1.2cm,align=center] {\small{\texttt{title:The \hspace{-0.15cm} Hobbit}}};

  \node (2i2)  [draw,black,minimum height=0.6cm,minimum width=2cm,xshift=1.9cm,yshift=0cm,right of = 2i1,text width=0.6\linewidth,align=center,fill=red!30] {};

@@

>>>>

  \node (v1) [draw,black,minimum height=0.9cm,minimum width=1cm,text width=0.4\linewidth,xshift=-4.3cm,align=center,yshift=0cm] {\small{\texttt{a:Person}}};

@@

      \node (1i1)  [draw,black,minimum height=0.6cm,minimum width=2cm,xshift=-0.5cm,text width=0.6\linewidth,yshift=0cm,align=center,fill=green!30] {\small{\texttt{$\rightarrow$ wrote b}}};

  \node (1i2)  [draw,black,minimum height=0.6cm,minimum width=2cm,xshift=1.9cm,yshift=0cm,right of = 1i1,text width=0.6\linewidth,align=center,fill=green!30] {\small{\texttt{year:1937}}};

  % 2
  \node (v) [draw,black,minimum height=0.9cm,minimum width=1cm,text width=0.4\linewidth,xshift=-4.3cm,align=center,yshift=-1.2cm] {\small{\texttt{vertex id}}};

@@

  \node (2i1)  [draw,black,minimum height=0.6cm,minimum width=2cm,xshift=-0.5cm,text width=0.6\linewidth,yshift=-1.2cm,align=center] {\small{\texttt{edge}}};

  \node (2i2)  [draw,black,minimum height=0.6cm,minimum width=2cm,xshift=1.9cm,yshift=0cm,right of = 2i1,text width=0.6\linewidth,align=center]  {\small{\texttt{property}}};

@@

    \node (t) [right of = b, xshift = 2cm] {};
    \node (t1) [right of = b1, xshift = 2cm] {};
  \node (t2) [right of = 4b1, xshift = 2cm] {};
